\documentclass[a4paper,12pt]{article}
\usepackage{TLCresume}
\begin{document}

%using zitemize instead of itemize will allow for tighter spacing before and after each line
\vspace*{6pt}
\subsection{{Product Lead}\hfill Aug 2024 -- Present}
\subtext{NDA Edtech \& HRtech Company (10+ years on market)}
\begin{zitemize}
\item Actively developing an end-to-end HR process automation product for a large enterprise as Product Manager: professionally conducting customer development, defining full project scope, initiating and executing the project, and communicating with stakeholders according to best practices; currently running test pilots with the same client.
\item Expertly conducted customer-development interviews with HRDs of companies with 10k--300k employees, identifying pain points, aligning requirements, and validating solution hypotheses.
\item Executed pilot implementations with large enterprise customers within tight timelines, demonstrating rapid MVP deployment.
\item Developed MVP of KPI decomposition module: delivered robust methodological framework leveraging decade-long expertise, validated efficacy, and advanced to full implementation with metric tracking.
\item Created MVP for test-content generation module across general education and niche domains: achieved 98\% accuracy validated by methodologists, reducing effort from three weeks (three methodologists) to one hour (one request).
\end{zitemize}

\vspace*{6pt}
\subsection{{Co-founder / Technical Product Manager}\hfill Apr 2024 -- May 2025}
\subtext{Shperling AI}
\begin{zitemize}
\item Led commercial development and client acquisition strategy: developed cold outreach scenarios and presented on-premise RAG solution, resulting in \$22,000 revenue from paid pilots and a \$5M startup valuation by private investors.
\item Delivered three on-premise RAG solutions (for internal support to travel agency, a Swiss consulting firm, and two fintech companies with 1M+ clients): managed data collection, set up solution architecture (DVC, Docker, PostgreSQL), , achieving 95\% accuracy on internal metrics and ~90\% relevance in client tests. Clients saved up to 50\% on support costs.
\item Initiated and supervised the creation of a text2SQL pipeline for a B2B retail startup: designed pipeline architecture, configured NLP modules and local SQL processing, reducing analytics turnaround time from 8 to 1 hour.
\item Organized business and customer development processes: set up manual and automated ABM outreach via LinkedIn (3,000+ contacts/month, 5\% conversion to conversations), conducted 50+ interviews with company representatives ($50M–$5B), forming a funnel where this leads converting to pilots.
\item Headed the prototype team (5 junior ML developers) and designed 5 prototypes of custom RAG architectures using Scrum: organized sprints and daily standups, with one prototype becoming the core of the commercial product.
\item Attracted an external AI industry advisor, accelerating feature development by 20\%: negotiated terms and integrated expert consultations into the development process, increasing client trust.
\item Pitched at key CIS conferences to audiences of 5,000+, generating 10+ pilot requests and expanding the partner network.
\item Led the preparation of the "LLM in Business" research (60 slides), laying the foundation for the Operation Co-Pilot strategy: defined key topics, organized data collection, and personally validated findings, helping to approve the new 2025 roadmap.
\item Winner of the CIS stage of GSEA ("Future Unicorn" status).
\end{zitemize}


\vspace*{6pt}
\subsection{{Head of Student Leadership Program}\hfill Dec 2023 -- May 2024}
\subtext{Daily Challenge}
\begin{zitemize}
\item Organized a centralized tracking and communication system for 100 students: developed and implemented a knowledge base using Notion, Airtable, and Make, enabling automatic participant status tracking and Telegram notifications.
\item Introduced a unified goal-setting framework and standardized reporting processes: merged scattered Telegram chats into a single ecosystem, which attracted an edtech project with a 40,000+ audience and ensured coverage of 80,000+ trained users.
\item Built a full HR funnel for monthly recruitment of 30+ students: developed unified message templates, standardized funnel stages, and conducted onboarding calls, accelerating new member adaptation and reducing churn.
\item Coordinated 10+ cross-functional teams (marketing, analytics, development, HR, etc.): held 8–12 online meetings per week, ensuring timely decision-making for both offline and online events and increasing participant engagement.
\end{zitemize}


\subsection{{BigData Analyst, Beeline Kazakhstan}\hfill June 2023 -- Nov 2023}
\subtext{Beeline is the largest Fintech company in Kazakhstan}
\begin{zitemize}
\item Interacted with production DB's based on HDFS, PySpark, Kafka, PostgreSQL to upload and send data.
\item Developed and brought to production SQL triggers for MyBeeline App.
\item Refactored Multisim Model, increased performance for 30 percent (F1 score)
\item Communicated with customers, promptly and successfully solved existing and new issues.
\end{zitemize}

%==================== 
% EXPERIENCE B 
%==================== 



\end{document}
