\documentclass[a4paper,12pt]{article}
\usepackage{TLCresume}
\begin{document}

%using zitemize instead of itemize will allow for tighter spacing before and after each line


\subsection{{MLE/ Co-founder, Shperling AI}\hfill Apr 2024 -- May 2025}
\subtext{Built enterprise-grade RAG solutions with 95\%+ accuracy and 25s response time}
\begin{zitemize}
\item Led and mentored a team of 5 ML engineers in building production RAG system: guided architecture decisions for Qwen-2.5-32B-Instruct-GPTQ-Int4 (local) and GPT-4o-mini (API) integration, achieving 92.4\% context recall and 87.3\% precision on RAGAS benchmarks. Coached team on vector store optimization with Milvus and BM25 hybrid search.
\item Established best practices and trained team on secure text2SQL development: implemented code review process focusing on SQL injection prevention and query validation, resulting in 82\% accuracy on complex queries (GROUP BY: 91.4\%, JOIN: 82.9\%) and 87.5\% Russian language support.
\item Designed and supervised implementation of microservices architecture, coaching junior developers on:
    \begin{itemize}
        \item Production-grade FastAPI development and Docker containerization
        \item Document processing pipelines with chunking optimization (rag-pilot)
        \item Secure database integration and query validation (text2sql)
        \item External API integration achieving 92\% relevance (funccal)
        \item Distributed storage systems with Milvus, MinIO, and ETCD
    \end{itemize}
\item Introduced MLOps practices through hands-on workshops: trained team on MLflow experiment tracking, W\&B monitoring, and CI/CD pipeline development. Reduced deployment issues by 40\% through systematic code review and documentation.
\end{zitemize}



\subsection{{BigData Analyst, Beeline Kazakhstan}\hfill 2023}
\subtext{Beeline is the largest Fintech company in Kazakhstan}
\begin{zitemize}
\item Interacted with production DB's based on HDFS, PySpark, Kafka, PostgreSQL to upload and send data.
\item Developed and brought to production SQL triggers for MyBeeline App.
\item Refactored  Multisim Model, increased performance for 30 percents(F1 score)
\item Communicated with customers, promptly and succesfully solved existing and new issues.
\end{zitemize}


% \vspace*{5pt}
% \subsection{{NTOContest AI track, Sber}\hfill 2023}
% \subtext{Largest AI contest for school students, Best Foreign solution}
% \begin{zitemize}
% \item Solved video classification, Video QA, table data tasks
% \item Got experience in building large neural nets, valuable
% experience in DL sphere.
% \end{zitemize}

\vspace*{5pt}
\subsection{{DANO Olympiad Winner, HSE and Tinkoff }\hfill 2022}
\subtext{Data Analysis National Olympiad}
\begin{zitemize}
\item Solved different analytical, data analysis tasks
\item Led team of 5 people, which made research on dataset of
movie ticket sales in 2020
\item Organized team and tracked a progress in Miro, Notion
\item Made EDA, Feature engineering, Data vizualizaon using
pandas/seaborn etc.
\end{zitemize}
\text {Totally -\textbf{ 23rd/7k+ place}(individual ranking), \textbf{9th/56 place}(team tour)
}

%==================== 
% EXPERIENCE B 
%==================== 



\end{document}
